Report on Lab 1 \& Lab 2 in EDA282, Parallel Computer Organization and Design

### 2014-10-14 lab/report/include/lab2.tex
task4

\section{Lab 2}
\label{sec:lab2}
For the second part of the lab the task is to parallelize a serial implementation of the Red-Back Gauss-Seidal algorithm. This is done using OpenMP (Open \textbf Multi-\textbf Processing) which is an API for forming multi-threaded programs in C, C++, and Fortran. This parallel version is evaluated using the same simulator and CCP:s as in \nameref{sec:lab1}.

@@

In \reffig{fig:lab2} results from running the parallelized version of the program in the simulator with different CCP:s and different matrix dimensions are shown. It can be seen that using MESI over MSI does not cause any noticeable boost in performance. This is because the gain of the extra E state becomes of no importance as the cache lines is in the M state most of the time. Some benefit of the E state can though be seen in Table~\ref{tbl:lab2} as the amount of \textit{WriteMisses} and \textit{InvalidationsSent} are a bit lower for MESI than MSI and the gap becomes bigger as the matrix size increases. This does not show in \reffig{fig:lab2} as the cycle count are not dominated by \textit{WriteMisses} and \textit{InvalidationsSent}.

Changing to MESI-MG yields a huge performance degradation of 420\%, 394\%, and 430\% for matrix size 25, 100, and 200 respectively. This comes from the sharing performed of the brim lines between threads. For each read of a dot in any of these lines, the dot gets migrated over to the thread performing the read. This frequent migration of dots generates a large amount of \textit{ReadMissesSerivcedByModfied} as can be seen in Table~\ref{tbl:lab2}. The overhead stays fairly constant compared to the other CCP:s when the matrix size increases. This is duo to the proportion of sharing between the threads stays the same.

@@

>>>>

\section{Lab 2}
\label{sec:lab2}
For the second part of the lab the task is to parallelize a serial implementation of the Red-Back Gauss-Seidal algorithm. This is done using OpenMP (Open \textbf Multi-\textbf Processing) which is an API for forming multi-threaded programs in C, C++, and Fortran. This parallel version is evaluated using the same simulator and CCPs as in \nameref{sec:lab1}.

@@

In \reffig{fig:lab2} results from running the parallelized version of the program in the simulator with different CCPs and different matrix dimensions are shown. It can be seen that using MESI over MSI does not cause any noticeable boost in performance. This is because the gain of the extra E state becomes of no importance as the cache lines is in the M state most of the time. Some benefit of the E state can though be seen in Table~\ref{tbl:lab2} as the amount of \textit{WriteMisses} and \textit{InvalidationsSent} are a bit lower for MESI than MSI and the gap becomes bigger as the matrix size increases. This does not show in \reffig{fig:lab2} as the cycle count are not dominated by \textit{WriteMisses} and \textit{InvalidationsSent}.

Changing to MESI-MG yields a huge performance degradation of 420\%, 394\%, and 430\% for matrix size 25, 100, and 200 respectively. This comes from the sharing performed of the brim lines between threads. For each read of a dot in any of these lines, the dot gets migrated over to the thread performing the read. This frequent migration of dots generates a large amount of \textit{ReadMissesSerivcedByModfied} as can be seen in Table~\ref{tbl:lab2}. The overhead stays fairly constant compared to the other CCPs when the matrix size increases. This is duo to the proportion of sharing between the threads stays the same.

@@

\par\noindent
\begin{minipage}[t]{.5\textwidth}
\begin{lstlisting}[language=C,frame=lrtb]
In readLine()
	if(MODIFIED) {...}
	if(EXCLUSIVE) {...}

	if(SHARED)
		return data

In writeRemoteAction()
	if(SHARED) {...}
\end{lstlisting}%
\end{minipage}%
\hfill
\begin{minipage}[t]{.5\textwidth}
\begin{lstlisting}[frame=lrtb]
In readLine()
	if(MODIFIED || EXCLUSIVE || OWNER) 
		state = OWNER
		return data

	if(SHARED)
	{}

In writeRemoteAction()
	if(SHARED || OWNER) {...}
\end{lstlisting}%
\end{minipage}%
